Stochastic Variance-Reduced Policy Gradient

### 2018-06-27 poster/poster.tex
first complete draft

\usepackage{tabu}
\usepackage{schemata}

@@

@@

\noindent\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=yellow!70!black!40!white, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlb{The easy part:}\\[.2cm]
%\begin{itemize}\compresslist
        $\bullet$~Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)\\[.15cm]
    $\bullet$~\textbf{SVRG} idea: combine \hlr{frequent \textbf{SG}} with \\\hlg{rare \textbf{FG}} into a corrected gradient estimator $\gradBlack{\vtheta}$\\[.15cm]
    $\bullet$~Two-time scales: $1$ \textbf{epoch} $=m$ \textbf{iterations}
%\end{itemize}
\end{tcolorbox}
\end{minipage}\hfill%
\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=orangep, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlo{Solving the RL challenges:}\\[.2cm]
%\begin{enumerate}\compresslist
    $\bullet$~Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)\\[.15cm]
    $\bullet$~Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$\\[.15cm]
	$\bullet$~Correct \chall{nonstationarity} with \textbf{importance weighting}	
%\end{enumerate}
\end{tcolorbox}
\end{minipage}

@@

\headerbox{Heuristics}{name=heuristics,column=3,span=1,row=0}{
	\begin{itemize}
		\item Adaptive step size
		\item Adaptive epoch size
		\item Normalized Importance Weighting
		\item Critic (baseline)
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Empirical Results}{name=emp,column=3,row=1,span=1,below=heuristics}{
	Direi che ci stanno 2 grafici, ma devo pensare a quali mettere

	Eventualmente saltano Related Work e le References
}

>>>>

\usepackage{tabu}

@@

\usepackage{stackengine}
\usepackage{scalerel}
\newcommand\dangersign[1][2ex]{%
	\renewcommand\stacktype{L}%
	\scaleto{\stackon[1.5pt]{\color{crimson}$\triangle$}{\tiny \bfseries{!}}}{#1}%
}

@@

\noindent\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=bluep, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlb{The easy part:}\\[.2cm]
%\begin{itemize}\compresslist
        $\bullet$~Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)\\[.15cm]
    $\bullet$~\textbf{SVRG} idea: combine \hlr{frequent \textbf{SG}} with \\\hlg{rare \textbf{FG}} into a corrected gradient estimator $\gradBlack{\vtheta}$\\[.15cm]
    $\bullet$~Two-time scales: $1$ \textbf{epoch} $=m$ \textbf{iterations}
%\end{itemize}
\end{tcolorbox}
\end{minipage}\hfill%
\begin{minipage}[t]{.48\textwidth}
\begin{tcolorbox}[left=0cm,right=0cm,top=0cm,bottom=0cm,colback=white, boxsep=.1cm, colframe=orangep, grow to left by=0cm, grow to right by=0cm]
\vspace*{-.11cm}\hspace*{-.11cm}\hlo{Solving the RL challenges:}\\[.2cm]
%\begin{enumerate}\compresslist
    $\bullet$~Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)\\[.15cm]
    $\bullet$~Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$\\[.15cm]
	$\bullet$~Correct \chall{nonstationarity} with \textbf{importance weighting}	
%\end{enumerate}
\end{tcolorbox}
\end{minipage}

@@

\headerbox{Heuristics}{name=heuristics,column=3,span=1,row=0}{
\noindent
Heuristics can improve performance in practice
	\begin{itemize}
		\item \hlb{Step size:} \textbf{ADAM} to counteract gradient variance\\
		\dangersign \hspace*{.05cm} FG and SG variance have completely different magnitude $\rightarrow$ use two separate annealing schedules $\alpha_{FG}$ and $\alpha_{SG}$
		\item \hlb{Epoch size:} cut epoch when the effective step size becomes too small
		\begin{equation*}
			\frac{\alpha_{FG}}{N} > \frac{\alpha_{SG}}{B} \implies \textbf{new epoch}
		\end{equation*}
		\item \hlb{Normalized importance weights:} reduce variance at the price of introducing a small bias
		\item \hlb{Critic:} an orthogonal variance reduction technique from the \textbf{PG} literature
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Empirical Results}{name=emp,column=3,row=1,span=1,below=heuristics}{

\noindent
\begin{tikzpicture}
	\node[inner sep=0pt] (picture1) {\includegraphics[width=.98\textwidth]{images/cartpole.pdf}};
	\node[above left] at ($(picture1.north west) + (2.7cm,-.6cm)$) {\textbf{Cart-Pole}};
\end{tikzpicture}%

\noindent
\begin{tikzpicture}
\node[inner sep=0pt] (picture2) {\includegraphics[width=0.98\textwidth]{images/swimmer.pdf}};
\node[above left] at ($(picture2.north west) + (2.8cm,-.5cm)$) {\textbf{Swimmer}};
\end{tikzpicture}%

\vspace*{-.3cm}

\noindent
\begin{tikzpicture}
\node[inner sep=0pt] (picture3) {\includegraphics[width=0.98\textwidth]{images/cheetah.pdf}};
\node[above left] at ($(picture3.north west) + (3.4cm,-.8cm)$) {\textbf{Half-Cheetah}};
\end{tikzpicture}%
}
